KidsAIR initial SUMs data work

### 2020-01-31 pm_summary.Rmd
more SUMs cleaning

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm < 500) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "SD Sample Days" = sd(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE)) %>% 
  select(-area) %>% 
  t()

kable(pm_summary, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")

>>>>

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  #filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm < 500) %>% 
  group_by(treatment) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "SD Sample Days" = sd(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE)) %>% 
  #select(-treatment) %>% 
  t()

kable(pm_summary, 
      digits = 1, align = "c")

### 2020-01-31 sums_data_cleaning.Rmd
more SUMs cleaning

# write_rds(sums_clean, "Output/sums_clean.rds")
```

>>>>

# write_rds(sums_clean, "Output/sums_clean.rds")

sums_clean <- read_rds("Output/sums_clean.rds")

time_diff_check <- sums_clean %>% 
  group_by(area, home) %>% 
  mutate(time_diff = lead(datetime_sums) - datetime_sums,
         time_diff_indicator = if_else(time_diff < 20, 1, 0)) %>% 
  filter(time_diff_indicator == 1) %>% 
  summarise(n())

time_diff_check_home <- sums_clean %>% 
  group_by(area, home) %>% 
  mutate(time_diff = lead(datetime_sums) - datetime_sums,
         time_diff_indicator = if_else(time_diff < 20, 1, 0)) %>% 
  filter(home == "WMA238")
```
